Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-27 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated what Gerardo and I discussed...

% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
\edef\docIndent{\the\parindent}
\edef\docParskip{\the\parskip}
\newenvironment{docParinfo}{%
 \edef\currentIndent{\the\parindent}
 \edef\currentParskip{\the\parskip}
 \setlength{\parindent}{\docIndent}%
 \setlength{\parskip}{\docParskip}
}{
 \setlength{\parindent}{\currentIndent}%
 \setlength{\parskip}{\currentParskip}
}
\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\newenvironment{compare}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
\newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
\NewDocumentEnvironment{compareText}{m m}{\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
\newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}

@@

\begin{compare}
\begin{oldText}{\andy}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures. 
\end{oldText}
\begin{newText}{\andy}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
intervals appearing in Eq.~(\ref{eq:interval-times})
is a natural consequence of the minus sign appearing in
Eq.~(\ref{eq:complement}).}  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures.
\end{newText}
\end{compare}

@@

To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
functions. A blurring function $f:\left[0,1\right]\rightarrow\mathscr{I}$
maps every real-valued probability $x\in\left[0,1\right]$ to a set
of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
where $\left[0,1\right]$ denotes the set of real-valued probabilities
which should not be considered as the interval-valued probability
$\unknown$. We also need a notion of norm to quantify the
distance between (pure or mixed) states. The norm of a pure state
$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
In addition, given any Hermitian operator~$A$, we consider the usual
operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
In fact, for any such matrix, including the density matrix~$\rho$,
the norm is the maximum absolute value of its eigenvalue. Then, a
finite-precision extension of Gleason's theorem can be stated as follows.

\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function
and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
probability measure induced by the Born rule for a given state~$\rho$.
Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}

@@

%% ajh: no abbreviations as first words of sentences.
Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
theorem in the sense that it accounts for a larger class of probability measures that includes
the conventional one as a limit. The theorem is however ``special'' in
the sense that it only applies to the particular class of QIVPMs
constructed by composing a blurring function with a conventional
quantum probability measure. QIVPMs constructed in this manner have
some peculiar properties that we examine next.

A blurring function is called \emph{ultramodular} if it satisfies
the following properties.

\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
  a collection of intervals $\mathscr{I}$ including $\imposs$ and
  $\necess$, a blurring function
  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
  ultramodular if:
\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \ultramodular(0)=\imposs\,,\\
 &  & \ultramodular(1)=\necess\,,\\
 &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
\end{eqnarray}
\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that
$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
\begin{equation}
\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

\noindent The first three constraints,
Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
counterpart of the convexity conditions,
Eq.~(\ref{eq:classicalconvex}) and
(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
these conditions guarantee that, for any conventional quantum
probability measure $\mu$, the composition $\ultramodular \circ \mu$
defines a valid QIVPM. Conversely, if for every quantum probability
measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the blurring
function~$f$ is an ultramodular function. Formally, we have the following
result.

@@

Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely, for the quantum case, we want
to show that if $\ultramodular$ is not ultramodular, then for
some quantum probability measure $\mu$, the composite
$\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
\[
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
\]
The induced map using the Born rule and blurred by $\ultramodular$,
$\ultramodular\circ\muB_{\rho}$, fails to satisfy
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
$P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
words, this induced map fails to be a QIVPM. For the classical case, if
$\ultramodular$ is not ultramodular, we also want to find a classical
probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$ such
that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
done by restricting our previous quantum probability measure
$\muB_{\rho}$ to the space of events  $\eventsC$  generated by the
mutually commuting projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and
$\proj{3}$.  The restricted function
$\mu=\muB_{\rho}|_{\eventsC}$ is then a classical probability
measure, and the induced map $\ultramodular\circ\mu$ fails to be
a classical IVPM for the same reason as in the quantum case.
%% ajh: sentence "This can be done..." is somehow garbled, tried to
%% fix.  $\eventsC$ is by DEFINITION a commuting subspace, so the
%% original sentence does not seem to have any meaning.  Are there
%% MORE mutually commuting projectors in $\eventsC$?  It would seem
%% that there are no others, so this is all confusing, as that would
%% make this sentence completely vacuous.

% In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
% there is always a state consistent with any composite QIVPM
% $\ultramodular\circ\muB_{\rho}$.  Moreover, the collection
% of states consistent with $\ultramodular\circ\muB_{\rho}$
% gets closer and closer to~$\rho$ as the intervals get narrower and
% narrower. Eventually, the collection of states collapses to the
% singleton set~$\left\{ \rho\right\} $ as the intervals become the
% infinitely precise intervals~$\mathscr{I}_{\infty}$. To precisely
% state this result, we introduce the norm of pure states and
% operators. The norm of a pure state~$\ket{\psi}$ is defined as usual
% $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
% given any Hermitian operator~$A$, we consider the usual operator norm
% $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
%   =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
% $2$-norm or the spectral
% norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
% Then, a version of Gleason's theorem can be stated as follow.

In other words, essential properties of QIVPMs constructed using
blurring functions can be gleaned from the properties of
ultramodular functions. The following is a most interesting property
in our setting.

@@

To summarize, a conventional quantum probability measure has an
uncountable range $[0,1]$. A QIVPM constructed by blurring such a
conventional quantum probability measure must also have an uncountable
range of intervals. Of course, any particular QIVPM, or any particular
experiment, will use a fixed collection of intervals appropriate for
the resources and precision of the particular experiment. 
%\gerardo{We need to explain physically what it means?}
% The essential reason for getting an uncountable number of intervals is
% the convexity condition we imposed on QIVPMs. This condition is widely
% used in the classical setting but it is possible that it should be
% modified or weakened in the quantum case. If we take this approach and 
% % Even if $\ultramodular$ has to be ultramodular to guarantee
% % $\ultramodular\circ\mu$ a QIVPM, the composited function
% % $\ultramodular\circ\mu$ may still be a QIVPM when $\ultramodular$ is
% % not ultramodular. In this case, the composited function
% % $\ultramodular\circ\mu$ could map to non-trivial finite number of
% % intervals. For example, we can 
% weaken the convexity condition, Eq.~(\ref{eq:iota-Inclusion}), we can
% recover QIVPMs that only require countable and even finite collections
% of intervals. Formally, we weaken the convexity condition to the
% following additive condition: for any numbers $x_{0}$ and
% $x_{1}\in\left[0,1\right]$, their sum $x_{0}+x_{1}\in\left[0,1\right]$
% implies
% \begin{equation}
% \ultramodular\left(x_{0}+x_{1}\right)\subseteq\ultramodular\left(x_{0}\right)+\ultramodular\left(x_{1}\right)\,.\label{eq:iota-add}
% \end{equation}
% Then, given a three-dimensional Hilbert space, if $\ultramodular$
% satisfies Eqs.~(\ref{eq:iota-constraints}) and
% Eq.~(\ref{eq:iota-add}), then $\ultramodular\circ\mu$ is a
% QIVPM~\cite{TaiThesis2018}.  For example, consider an orthonormal
% basis $\{\ket{0},\ket{1},\ket{2}\}$, two states
% $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
% and
% $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,
% and a set of intervals:
% \begin{equation}
% \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
%  & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
% \end{aligned}
% \end{equation}
% Since the interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
% defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
% and Eq.~(\ref{eq:iota-add})~\cite{TaiThesis2018}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
% and $\ultramodular_{2}\circ\muB_{\rho_{1}}$ are both
% QIVPMs.
% \begin{table}
% \caption{\label{tab:I_2}A interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}

% \hfill{}%
% \begin{minipage}[t]{2.5cm}%
% \begin{center}
% \begin{tabular}{cc}
% \toprule 
% \addlinespace
% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
% \midrule
% \midrule 
% \addlinespace
% $x=0$ & $\imposs$\tabularnewline\addlinespace
% \midrule 
% \addlinespace
% $0<x\le\tfrac{1}{8}$ & $\left[0,\tfrac{1}{4}\right]$\tabularnewline\addlinespace
% \midrule 
% \addlinespace
% $\tfrac{1}{8}<x<\tfrac{3}{8}$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$\tabularnewline\addlinespace
% \midrule 
% \addlinespace
% $\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
% \bottomrule
% \end{tabular}
% \par\end{center}%
% \end{minipage}\hfill{}%
% \begin{minipage}[t]{2.5cm}%
% \begin{center}
% \begin{tabular}{cc}
% \toprule 
% \addlinespace
% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
% \midrule
% \midrule 
% \addlinespace
% $\tfrac{5}{8}<x<\tfrac{7}{8}$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
% \midrule 
% \addlinespace
% $\tfrac{7}{8}\le x<1$ & $\left[\tfrac{3}{4},1\right]$\tabularnewline\addlinespace
% \midrule 
% \addlinespace
% $x=1$ & $\necess$\tabularnewline\addlinespace
% \bottomrule
% \end{tabular}
% \par\end{center}%
% \end{minipage}\hfill{}
% \end{table}
% Given any one-dimensional projector $\proj{\psi}$, we have $\muB_{\rho_{0}}\left(\proj{\psi}\right)=\frac{1}{3}$
% so that $\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
% On the other hand, 
% \begin{eqnarray*}
% \muB_{\rho_{1}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
% \end{eqnarray*}
% is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
% $\muB_{\rho_{1}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)$.
% According to the complement condition, Eq.~(\ref{eq:complement}), we
% also have
% $\muB_{\rho_{1}}\left(P\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(P\right)\right)$
% for any two-dimensional projector~$P$. Hence,
% $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\muB_{\rho_{0}},\events\right)$,
% and Thm.~\ref{thm:Finite-precision-Gleason} asserts that
% $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is less than or equal to the
% maximum length of intervals $\frac{1}{2}$.  This is true because the
% exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
% $\frac{1}{24}$.

>>>>

% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
\edef\docIndent{\the\parindent}
\edef\docParskip{\the\parskip}
\newenvironment{docParinfo}{%
 \edef\currentIndent{\the\parindent}
 \edef\currentParskip{\the\parskip}
 \setlength{\parindent}{\docIndent}%
 \setlength{\parskip}{\docParskip}
}{
 \setlength{\parindent}{\currentIndent}%
 \setlength{\parskip}{\currentParskip}
}
\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\newenvironment{compare}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
\newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
\NewDocumentEnvironment{compareText}{m m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
\newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}

@@

\begin{compare}
\begin{oldText}{\andy}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
intervals appearing in Eq.~(\ref{eq:interval-times})
is a natural consequence of the minus sign appearing in
Eq.~(\ref{eq:complement}).}  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures.
\end{oldText}
\begin{newText}{\yutsung}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  {\color{purple}Note that we need to
consider $x\le0$ case in Eq.~(\ref{eq:interval-times}) because of the minus sign
appearing in
Eq.~(\ref{eq:complement}).}  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures.
\end{newText}
\end{compare}

@@

\begin{compare}
\begin{oldText}{\andy}
To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{blurring}
functions. A blurring function} $f:\left[0,1\right]\rightarrow\mathscr{I}$
maps every real-valued probability $x\in\left[0,1\right]$ to a set
of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
where $\left[0,1\right]$ denotes the set of real-valued probabilities
which should not be considered as the interval-valued probability
$\unknown$. We also need a notion of norm to quantify the
distance between (pure or mixed) states. The norm of a pure state
$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
In addition, given any Hermitian operator~$A$, we consider the usual
operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
In fact, for any such matrix, including the density matrix~$\rho$,
the norm is the maximum absolute value of its eigenvalue. Then, a
finite-precision extension of Gleason's theorem can be stated as follows.
\end{oldText}
\begin{newText}{\andy}
To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{interval}
maps. A interval map} $f:\left[0,1\right]\rightarrow\mathscr{I}$
maps every real-valued probability $x\in\left[0,1\right]$ to a set
of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
where $\left[0,1\right]$ denotes the set of real-valued probabilities
which should not be considered as the interval-valued probability
$\unknown$. We also need a notion of norm to quantify the
distance between (pure or mixed) states. The norm of a pure state
$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
In addition, given any Hermitian operator~$A$, we consider the usual
operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
In fact, for any such matrix, including the density matrix~$\rho$,
the norm is the maximum absolute value of its eigenvalue. Then, a
finite-precision extension of Gleason's theorem can be stated as follows.
\end{newText}
\end{compare}

\begin{compareNextpage}
\begin{oldText}{\andy}
\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}blurring function}
and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
probability measure induced by the Born rule for a given state~$\rho$.
Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
\end{oldText}
\begin{newText}{\andy}
\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}interval map}
and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
probability measure induced by the Born rule for a given state~$\rho$.
Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
\end{newText}
\end{compareNextpage}

@@

\begin{compare}
\begin{oldText}{\andy}
Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
theorem in the sense that it accounts for a larger class of probability measures that includes
the conventional one as a limit. The theorem is however ``special'' in
the sense that it only applies to the particular class of QIVPMs
constructed by composing a {\color{blue}blurring function} with a conventional
quantum probability measure. QIVPMs constructed in this manner have
some peculiar properties that we examine next.

A {\color{blue}blurring function} is called \emph{ultramodular} if it satisfies
the following properties.

\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
  a collection of intervals $\mathscr{I}$ including $\imposs$ and
  $\necess$, a {\color{blue}blurring function}
  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
  ultramodular if:
\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \ultramodular(0)=\imposs\,,\\
 &  & \ultramodular(1)=\necess\,,\\
 &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
\end{eqnarray}
\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that
$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
\begin{equation}
\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

\noindent The first three constraints,
Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
counterpart of the convexity conditions,
Eq.~(\ref{eq:classicalconvex}) and
(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
these conditions guarantee that, for any conventional quantum
probability measure $\mu$, the composition $\ultramodular \circ \mu$
defines a valid QIVPM. Conversely, if for every quantum probability
measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}blurring
function}~$f$ is an ultramodular function. Formally, we have the following
result.
\end{oldText}
\begin{newText}{\andy}
Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
theorem in the sense that it accounts for a larger class of probability measures that includes
the conventional one as a limit. The theorem is however ``special'' in
the sense that it only applies to the particular class of QIVPMs
constructed by composing a {\color{blue}interval map} with a conventional
quantum probability measure. QIVPMs constructed in this manner have
some peculiar properties that we examine next.

A {\color{blue}interval map} is called \emph{ultramodular} if it satisfies
the following properties.

\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
  a collection of intervals $\mathscr{I}$ including $\imposs$ and
  $\necess$, a {\color{blue}interval map}
  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
  ultramodular if:
\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \ultramodular(0)=\imposs\,,\\
 &  & \ultramodular(1)=\necess\,,\\
 &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
\end{eqnarray}
\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that
$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
\begin{equation}
\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

\noindent The first three constraints,
Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
counterpart of the convexity conditions,
Eq.~(\ref{eq:classicalconvex}) and
(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
these conditions guarantee that, for any conventional quantum
probability measure $\mu$, the composition $\ultramodular \circ \mu$
defines a valid QIVPM. Conversely, if for every quantum probability
measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}interval
map}~$f$ is an ultramodular function. Formally, we have the following
result.
\end{newText}
\end{compare}

@@

Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely, for the quantum case, we want
to show that if $\ultramodular$ is not ultramodular, then for
some quantum probability measure $\mu$, the composite
$\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
\[
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
\]
The induced map using the Born rule and blurred by $\ultramodular$,
$\ultramodular\circ\muB_{\rho}$, fails to satisfy
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
$P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
words, this induced map fails to be a QIVPM. For the classical case, if
$\ultramodular$ is not ultramodular, we also want to find a classical
probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$ such
that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
done by restricting our previous quantum probability measure
$\muB_{\rho}$ to the space of events  $\eventsC$  generated by the
mutually commuting projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and
$\proj{3}$.  The restricted function
$\mu=\muB_{\rho}|_{\eventsC}$ is then a classical probability
measure, and the induced map $\ultramodular\circ\mu$ fails to be
a classical IVPM for the same reason as in the quantum case.

\begin{compare}
\begin{oldText}{\andy}
In other words, essential properties of QIVPMs constructed using
{\color{blue}blurring function}s can be gleaned from the properties of
ultramodular functions. The following is a most interesting property
in our setting. 
\end{oldText}
\begin{newText}{\andy}
In other words, essential properties of QIVPMs constructed using
{\color{blue}interval map}s can be gleaned from the properties of
ultramodular functions. The following is a most interesting property
in our setting. 
\end{newText}
\end{compare}

@@

\begin{compare}
\begin{oldText}{\andy}
To summarize, a conventional quantum probability measure has an
uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}blurring} such a
conventional quantum probability measure must also have an uncountable
range of intervals. Of course, any particular QIVPM, or any particular
experiment, will use a fixed collection of intervals appropriate for
the resources and precision of the particular experiment. 
\end{oldText}
\begin{newText}{\andy}
To summarize, a conventional quantum probability measure has an
uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}?????} such a
conventional quantum probability measure must also have an uncountable
range of intervals. Of course, any particular QIVPM, or any particular
experiment, will use a fixed collection of intervals appropriate for
the resources and precision of the particular experiment. 
\end{newText}
\end{compare}
